Fisheries management when quotas are costly to change

### 2014-08-11 manuscripts/presentation.Rmd
update presentation

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  revealjs_presentation:
    theme: serif
    self_contained: true
    incremental: true
    transition: none
    pandoc_args: ["--css", "components/style.css"]
author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth

@@

> ## As ecologists, we've ever focused on accounting for _ecological_ dynamics

@@

- subject to multiplicitive log-normal growth shocks $Z_t$

@@

- Small adjustments are very cheap
- Large adjustments are very expensive
- Closest to typical assumptions of quadratic costs on harvest/effort (but hear it is the _change_ in harvest/effort)

@@

- A fixed transaction fee for any change to policy, independent of size.

@@

@@

>>>>

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  revealjs_presentation:
    theme: serif
    self_contained: true
    incremental: true
    transition: none
    pandoc_args: ["--css", "components/style.css"]
author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviere, Alan Hastings, Paul Armsworth

@@

> ## As ecologists, we've always focused on accounting for _ecological_ dynamics

@@

- subject to multiplicative log-normal growth shocks $Z_t$

@@

- Small adjustments are very cheap
- Large adjustments are very expensive
- Closest to typical assumptions of quadratic costs on harvest/effort (but here it is the _change_ in harvest/effort)

@@

- A fixed transaction fee for any change to policy, independent of size (or sign) of the change.

@@

- All forms will create complete resistance to change if the costs are high enough
- But how do we compare across forms that have different units and different coefficients?

@@

## A 'Pretty Darn Good' Working Group

![](components/images/pdg-group.jpg)
